Legends for Figures

### 2019-01-20 Manuscript/Figures/figure_legends.Rmd
Fix Figure 2 legend

**Figure 2. Diagram of the three predictor types considered when assessing the relationship between TAD boundaries and genomic annotations.** The _overlap count_ (OC) predictors were calculated by considering the total number of elemental regions that overlapped with each genomic bin. The _overlap percent_ (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin and dividing by the total bin width. The _distance_ predictors were calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest elemental region of interest. The two green segments directly below the rightmost enlarged figure represent the center of the overlapping regions defining the respective genomic annotations.

>>>>

**Figure 2. The three predictor types considered when quantifying the association between TAD boundaries and genomic annotations.** The _overlap count_ (OC) predictors consider the total number of genomic features that overlapped with each genomic bin. The _overlap percent_ (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin by the total bin width. The _distance_ predictors were calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest genomic feature.
